Commit Rater

### 2015-08-26 presentations/paper/conclusion.tex
Make conclusion a little weaker

Only one of our research question has been answered positively: ``good'' commits were recognized by the aforementioned criteria. However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.

>>>>

Only one of our research question has been answered vaguely positively: ``good'' commits were recognized by the aforementioned criteria. However, we were unable to draw further conclusions from analysis on higher levels. Additionally, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.
